Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-07-06 manuscript.Rmd
Remove redactions

This work is a reproducible manuscript. All code and analyses can be found at:
[redacted for blind review].

@@

\noindent[redacted for blind review]

<!-- This work was completed in part as coursework done by lead author M. Chiovaro in -->
<!-- the “Applications of Nonlinear Time Series Analysis” graduate course at the -->
<!-- University of Connecticut (co-taught by coauthor A. Paxton and Steven J. -->
<!-- Harrison). -->

>>>>

This work is a reproducible manuscript. All code and analyses can be found at:
www.github.com/mchiovaro/arab-spring.

@@

This work was completed in part as coursework done by lead author M. Chiovaro in
the “Applications of Nonlinear Time Series Analysis” graduate course at the
University of Connecticut (co-taught by coauthor A. Paxton and Steven J.
Harrison).
